Adversarial Training against Systematic Uncertainty

### 2016-09-06 tex/paper.tex
save

In this section, we show that in the setting of
Algorithm~\ref{alg:adversarial-training} where ${\cal L}_f$ and ${\cal L}_r$ are
respectively set to expected value of the negative log-likelihood of $Y|X$ under
$f$ and of $Z|f(X;\theta_f)$ under $r$, the procedure converges to a classifier
$f$ which is a pivotal quantity in the sense of Eqn.~\ref{eqn:criterion}.
Propositions below are derived in a non-parametric setting, by assuming that
both $f$ and $r$ have enough capacity. Results hold for a nuisance parameter $Z$
taking either categorical values or continuous values within a bounded support.
By abuse of notation, $H(p_Z)$ denotes the differential entropy in this latter
case. Finally, by construction, we require the uniform prior $p(z)$ over the
values $z \in {\cal Z}$ of the nuisance parameter.

@@

\glnote{We should make it clearer what {\it classification optimality} means: it
is with respect to $Y|X=x$  when  $x$ results from $z\sim p_Z, x \sim X_z$.
This is often strictly different from optimality with respect to $Y|X=x,Z=z$ for the true value $z$.}

>>>>

In this section, we show that in the setting of
Algorithm~\ref{alg:adversarial-training} where ${\cal L}_f$ and ${\cal L}_r$ are
respectively set to expected value of the negative log-likelihood of $Y|X$ under
$f$ and of $Z|f(X;\theta_f)$ under $r$, the procedure converges to a classifier
$f$ which is a pivotal quantity in the sense of Eqn.~\ref{eqn:criterion}.

In this setting, the nuisance parameter $Z$ is considered as a random variable,
for which we require the uniform prior $p(z)$ (for $z$ in ${\cal Z}$).  Results
hold for a nuisance parameter $Z$ taking either categorical values or continuous
values within a bounded support. By abuse of notation, $H(p_Z)$ denotes the
differential entropy in this latter case. Finally, propositions below are derived in a
non-parametric setting, by assuming that both $f$ and $r$ have enough capacity.

@@
